What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2024-11-28 Manuscript files/Manuscript.qmd
Tables

In the following, we showcase the application of cjbart to data provided by Prof. Dr. Paul Thurner and Fabian Haggerty from the Geschwister-Scholl-Institute of Political Science, LMU Munich.
The data were first described in CITE.
In their work, CITE aimed at investigating which attributes citizens from five different NATO-member countries (United States [US], United Kingdom [UK], Germany, Italy, and France) deem important when deciding whether Ukraine should be supported economically and militarily against the Russian aggression.
For this, CITE conducted a conjoint experiment where $N = 10,011$ participants from the five countries chose one of two possible profiles. 
In these profiles, nine different attributes with varying attribute levels were manipulated randomly to indicate the consequences that a support of Ukraine would entail if the profile was chosen.
The different attributes, their corresponding levels, and the reference categories we used for our analyses are shown in TABLE.
Additionally, subject-level covariates were assessed, for example, participants' age, gender, political orientation, or their country of origin (of the five countries mentioned above).

```{r attributes, echo=FALSE}
#| output: asis
library(kableExtra)

@@

>>>>

In the following, we showcase the application of cjbart to data provided by Prof. Dr. Paul Thurner and Fabian Haggerty from the Geschwister-Scholl-Institute of Political Science, LMU Munich.
The data were first described in CITE.
In their work, CITE aimed at investigating which attributes citizens from five different NATO-member countries (United States [US], United Kingdom [UK], Germany, Italy, and France) deem important when deciding whether Ukraine should be supported economically and militarily against the Russian aggression.
For this, CITE conducted a conjoint experiment where $N = 10,011$ participants from the five countries chose one of two possible profiles. 
In these profiles, nine different attributes with varying attribute levels were manipulated randomly to indicate the consequences that a support of Ukraine would entail if the profile was chosen.
The different attributes, their corresponding levels, and the reference categories we used for our analyses are shown in @tbl-attributes.
Additionally, subject-level covariates were assessed, for example, participants' age, gender, political orientation, or their country of origin (of the five countries mentioned above).

```{r attributes, echo=FALSE}
#| output: asis
#| label: tbl-attributes
library(kableExtra)

@@

```{r covariates, echo=FALSE}
#| output: asis
library(kableExtra)
